Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-12 results.tex
Edited section 4.2.2
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1049 ccdd05d5-56c1-461a-bf98-85f6876523b4
Changed 2 subsubsections to paragraphs
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1050 ccdd05d5-56c1-461a-bf98-85f6876523b4
Revised section 4.3
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1051 ccdd05d5-56c1-461a-bf98-85f6876523b4

\subsection{Setup}

@@

\subsubsection{Effect of \SVD\ tolerance}

@@

\subsubsection{Effect of interpolation filter length}

Next, keeping the \SVD\ tolerance fixed at $\left(1-10^{-6}\right)$, we studied the
impact of the length $N^\shortuparrow$ of the interpolation filter.  The results are in
figure \ref{fig:hist-interpolate}.  We find that a filter length of 16 is sufficient
to meet our target mismatch of 0.003.

@@

We are now prepared to offer the estimated computational cost of filtering this
sub-bank of templates compared to other methods.  We used the results of the
previous subsections to set the \SVD\ tolerance to $1-10^{-4}$  and the
interpolation filter length to 16. Table \ref{table:flops} lists the
theoretical costs for filtering this sub-bank. Both the \FD\ method and \lloid\
are five orders of magnitude faster than the conventional \TD\ method.
However, the \FD\ method has a latency of over half of an hour, whereas \lloid\
has no latency at all.
%
\begin{table}
\caption{\label{table:flops}Computational cost in \flops\ of the \TD\ method, the \FD\ method, and \lloid\ for the bank of $2 \times 657$ templates sampled at 4096 Hz for chirp masses $1.1955 \leqslant \mathcal{M} / M_\odot \leqslant 1.2045$.  A block size of $D = 2 N$ is used for the \fft{}s in the \FD\ method.}
\begin{tabular}{lll}
\tableline\tableline
Method & \flops\ & Latency (s) \\
\tableline
Time domain (\TD) & $2.4\times10^{13}$ & 0 \\
Frequency domain (\FD) & $2.6\times10^8$ & 2201 \\
\lloid\ (this work) & $4.7\times10^8$ & 0 \\
\tableline
\end{tabular}
\end{table}

>>>>

\subsection{Setup}
\label{sec:bank-setup}

@@

\paragraph{Effect of \SVD\ tolerance}

@@

\paragraph{Effect of interpolation filter length}

Next, keeping the \SVD\ tolerance fixed at $\left(1-10^{-6}\right)$, we studied the
impact of the length $N^\shortuparrow$ of the interpolation filter.  The mismatch as
a function of $N^\shortuparrow$ is shown in figure~\ref{fig:hist-interpolate}.  The
mismatch saturates at $\sim 2 \times 10^{-4}$ with $N^\shortuparrow = 64$.  We find
that a filter length of 16 is sufficient to meet our target mismatch of 0.003.

@@

We are now prepared to offer the estimated computational cost of filtering this
sub-bank of templates compared to other methods.  We used the results of the
previous subsections to set the \SVD\ tolerance at $\left(1-10^{-4}\right)$ and the
interpolation filter length to 16. Table \ref{table:flops} shows the computational cost
in \flops\ for this sub-bank.  Fort the \FD\ method, an \fft\ block size of $\fftblock = 
2 \tmpsamps$ is assumed, resulting in a latency of $\left(\tmpsamps f^0\right)$
seconds.  Both the \FD\ method and \lloid\ are five orders of magnitude faster than
the conventional \TD\ method.  However, the \FD\ method has a latency of over half of an
hour, whereas \lloid\ has no latency at all.
%
\begin{table}
\caption{\label{table:flops}Computational cost in \flops\ of the \TD\ method, the \FD\ method, and \lloid\ for the sub-bank described in section~\ref{sec:bank-setup}.}
\begin{tabular}{lll}
\tableline\tableline
Method & \flops\ & Latency (s) \\
\tableline
Time domain & $2.4\times10^{13}$ & 0 \\
Frequency domain & $2.6\times10^8$ & 2201 \\
\lloid\ (this work) & $4.7\times10^8$ & 0 \\
\tableline
\end{tabular}
\end{table}
